Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Analytic Askaryan Signals

### 2024-07-30 template.tex
updates: fixed some typos and correcting some units factors, factors of 2
calculated new results given that there was a missing factor of 2 near the Dawson Function

S(f) = E_0 (2\pi)^{3/2} j f e^{-2\pi^2 f^2 \sigma_t^2}

@@

S(f) = E_0 (2\pi)^{3/2} j f e^{-\frac{1}{2}\left(f/\sigma_f\right)^2}

@@

Inserting $S(f)$ into Eq. \ref{eq:sa_1}, $s_{\rm a}(t)$ is

@@

s_{\rm a}(t) = \frac{E_0 \sigma_t^2 (2\pi)^{3/2}}{\pi} \frac{d}{dt}\int_0^{\infty} e^{-\frac{1}{2}\left(f/\sigma_f\right)^2} e^{2\pi j f t} df \label{eq:sa_3}

@@

\item Let the integral in Eq. \ref{eq:sa_3} be $I$, $k^2/4 = \frac{1}{2}\left(f/\sigma_f^2\right)$, and $x = t/(\sqrt{2}\sigma_t)$.  The real and imaginary parts of $I$ are

@@

\Re\lbrace I \rbrace &= \frac{\sigma_f}{\sqrt{2}} \int_0^{\infty} e^{-k^2/4}\cos(kx) dk \\
\Im\lbrace I \rbrace &= \frac{\sigma_f}{\sqrt{2}} \int_0^{\infty} e^{-k^2/4}\sin(kx) dk \\

@@

\Re\lbrace I \rbrace = \sqrt{\frac{\pi}{2}} \sigma_f e^{-\frac{1}{2}\left(t/\sigma_t\right)^2}

@@

The imaginary part of $I$ is proportional to $D(x)$, known as \textit{Dawson's integral:}

@@

\Im{I} = \sqrt{2}\sigma_f D(x)

@@

s_a(t) = -E_0 \left(t e^{-\frac{1}{2}\left(t/\sigma_t\right)^2} - \frac{j\sigma_t}{\sqrt{2\pi}} \frac{dD(x)}{dx}\right) \label{eq:sa_4}

@@

The signal envelope is $|s_a(t)|$:
\mathcal{E}_s(t) = E_0 \left(t^2 e^{-\left(t/\sigma_t\right)^2} + \frac{\sigma_t^2}{2\pi} \left(\frac{dD(x)}{dx}\right)^2\right)
It is important to note that, though $D(x)$ is not evaluated analytically, a high-precision algorithm for computing $D(x)$ was given in \cite{10.1063/1.4822832}.  Note that $s_a(0) \neq 0$, since $D(x) = 1 - 2x D(x)$.

@@

r_a(t) * \Re\lbrace s_a(t)\rbrace =& \sqrt{\frac{\pi}{2}} E_0 R_0 \sigma_t^2 \sqrt{2} e^{-\gamma t} e^{2\pi j f_0 t} \frac{dQ}{dz_0} \\
Q(z_0) &= e^{z_0^2/4} \erfc(z_0/2)

@@

Note that there is an extra factor of $\sqrt{2}\sigma_t$ to account for the measure $dt$ in the convolution upon changing the convolution integral from $dt$ to $dx$.

@@

r_a(t) * \Im\lbrace s_a(t)\rbrace = \frac{j}{2}\sqrt{\frac{\pi}{2}} E_0 R_0 \sigma_t^2 \sqrt{2} x e^{-x^2} Q(z_0)

@@

Note that the complementary error function is an \textit{entire function}, so $dQ/dz_0$ is defined for all $z_0$.

@@

r_a (t) * s_a(t) = \sqrt{\frac{\pi}{2}} E_0 R_0 \sigma_t^2 \sqrt{2} \\ \left(e^{-\gamma t} e^{2\pi j f_0 t} \frac{dQ}{dz_0} - \frac{1}{2} x e^{-x^2} Q(z_0) \right)

@@

\mathcal{E}_{r * s}(t) = \sqrt{\frac{\pi}{4}} E_0 R_0 \sigma_t^2 \\ \left|e^{-\gamma t} e^{2\pi j f_0 t} \frac{dQ}{dz_0} - \frac{1}{2} x e^{-x^2} Q(z_0) \right|

>>>>

S(f) = E_0 \sigma_t^3 (2\pi)^{3/2} j f e^{-2\pi^2 f^2 \sigma_t^2}

@@

S(f) = E_0 \sigma_t^3 (2\pi)^{3/2} j f e^{-\frac{1}{2}\left(f/\sigma_f\right)^2}

@@

Inserting $S(f)$ into Eq. \ref{eq:sa_2}, $s_{\rm a}(t)$ is

@@

s_{\rm a}(t) = \frac{E_0 \sigma_t^3 (2\pi)^{3/2}}{\pi} \frac{d}{dt}\int_0^{\infty} e^{-\frac{1}{2}\left(f/\sigma_f\right)^2} e^{2\pi j f t} df \label{eq:sa_3}

@@

\item Let $k^2/4 = \frac{1}{2}\left(f/\sigma_f^2\right)$, and $x = t/(\sqrt{2}\sigma_t)$.  Equation \ref{eq:sa_3} can be broken into real and imaginary parts:

@@

s_{\rm a}(t) &= \frac{E_0 \sigma_{\rm t}}{\sqrt{2\pi}}\frac{dI}{dx} \\
\Re\lbrace I \rbrace &= \int_0^{\infty} e^{-k^2/4}\cos(kx) dk \\
\Im\lbrace I \rbrace &= \int_0^{\infty} e^{-k^2/4}\sin(kx) dk

@@

\Re\lbrace I \rbrace = \sqrt{\pi} e^{-x^2}

@@

The imaginary part of $I$ is proportional to \textit{Dawson's integral, $D(x)$:}

@@

\Im\lbrace I\rbrace = 2 D(x)

@@

s_a(t) = -E_0 \left(t e^{-\frac{1}{2}\left(t/\sigma_t\right)^2} - \frac{2 j\sigma_t}{\sqrt{2\pi}} \frac{dD(x)}{dx}\right) \label{eq:sa_4}

@@

The signal envelope is $|s_a(t)|$.  It is important to note that, though $D(x)$ is not evaluated analytically, a high-precision algorithm for computing $D(x)$ was given in \cite{10.1063/1.4822832}.  Note that $s_a(0) \neq 0$, since $dD(x)/dx = 1 - 2x D(x)$.

@@

r_a(t) * \Re\lbrace s_a(t)\rbrace =& -\sqrt{\pi} E_0 R_0 \sigma_t^2 e^{-\gamma t} e^{2\pi j f_0 t} \frac{dQ}{dz_0} \label{eq:result1} \\
Q(z_0) &= e^{z_0^2/4} \erfc(z_0/2) \label{eq:result2}

@@

@@

r_a(t) * \Im\lbrace s_a(t)\rbrace = -\sqrt{\frac{\pi}{2}} R_0 E_0 \sigma_t t e^{-\frac{1}{2}(t/\sigma_t)^2} Q(z_0) \label{eq:result3}

@@

Note that the complementary error function and Gaussian functions are \textit{entire functions}, so $dQ/dz_0$ is defined for all $z_0$.
\item The results in Eqs. \ref{eq:result1}-\ref{eq:result3} may be expressed in terms of $s(t)$ and $r_{\rm a}(t)$:
r_a(t) * \Re\lbrace s_a(t)\rbrace =& -\sqrt{\pi} E_0 \sigma_t^2 r_{\rm a}(t) \frac{dQ}{dz_0} \\
r_a(t) * \Im\lbrace s_a(t)\rbrace =& \sqrt{\frac{\pi}{2}} R_0 \sigma_t s(t) Q(z_0)

@@

r_a (t) * s_a(t) = -\sqrt{\pi} E_0 \sigma_t^2 r_{\rm a}(t) \frac{dQ}{dz_0} \\ + j\sqrt{\frac{\pi}{2}} R_0 \sigma_t s(t) Q(z_0)

@@

\mathcal{E}_{r * s}(t) = \frac{1}{2}|r_{\rm a}(t) * s_{\rm a}(t)|
